An Empirical Analysis of the Role of Energy in Economic Growth

### 2018-09-12 README.Rmd
Updates to vignette.

---
output: github_document
---

@@

The MacroGrowth package provides sophisticated tools for fitting macroeconomic 
growth models to data. MacroGrowth has several desirable features for economic modelers:

@@

The functions in this package were developed for and used first in the paper
Heun, M.K., J. Santos, P.E. Brockway, R. Pruim, T. Domingos, and M. Sakai.
"From Theory to Econometrics to Energy Policy: 
Cautionary Tales for Policymaking Using Aggregate Production Functions".
*Energies*, pp. 1-44, 10 (203), 2017.
<http://doi.org/10.3390/en10020203>.

@@

You can install MacroGrowth from github with:

```{r gh-installation, eval = FALSE}
# install devtools if not already installed
# install.packages("devtools")
devtools::install_github("EconModels/MacroGrowth")
# To get vignettes built locally, use
devtools::install_github("EconModels/MacroGrowth", build_vignettes = TRUE)
```

>>>>

---
output: github_document
bibliography: vignettes/References.bib
---

@@

The `MacroGrowth` package provides sophisticated tools for fitting macroeconomic 
growth models to data. 
`MacroGrowth` has several desirable features for economic modelers:

@@

The functions in this package were developed for and used first in 
Heun et al. [-@Heun:2017].

@@

You can install `MacroGrowth` from github with:

```{r gh-installation, eval = FALSE}
# install devtools if not already installed
# install.packages("devtools")
devtools::install_github("EconModels/MacroGrowth")
# To build vignettes locally, use
devtools::install_github("EconModels/MacroGrowth", build_vignettes = TRUE)
```

## More Information

Find more information, including vignettes and function documentation at 
<https://econmodels.github.io/MacroGrowth/>

## References
